Natural Stories model analyses

### 2022-08-10 Analysis/models.Rmd
Added some more formulae including test for non-linearity in surprisal

```{r maze-formulae, echo=T}
#no hierarchical, has freq x len interaction
formula_interact <- rt ~ s(surprisal, bs="cr", k=20)+
                     ti(freq, bs="cr") + 
                     ti(len, bs="cr")+
                     ti(freq,len, bs="cr")+
                     s(prev_surp, bs="cr", k=20)+
                     ti(prev_freq, bs="cr")+
                     ti(prev_len, bs="cr")+
                     ti(prev_freq, prev_len, bs="cr")

@@

gam_ngram_2 <- gam(formula_no_interact, data=ngram_mean_data, method="REML")
gam_grnn_2 <- gam(formula_no_interact, data=grnn_mean_data, method="REML")
gam_txl_2 <- gam(formula_no_interact, data=txl_mean_data, method="REML")
gam_gpt_no_interact <- gam(formula_no_interact, data=gpt_mean_data, method="REML")

@@

>>>>

```{r maze-formulae, echo=T}

#no hierarchical, has freq x len interaction
formula_no_interact_linear_surprisal <- rt ~ surprisal +
                     ti(freq, bs="cr") + 
                     ti(len, bs="cr")+
                     ti(freq,len, bs="cr")+
                     prev_surp +
                     ti(prev_freq, bs="cr")+
                     ti(prev_len, bs="cr")+
                     ti(prev_freq, prev_len, bs="cr")

# no hierarchical, NO freq x len interaction
formula_no_interact_plus_linear_surprisal <- rt ~ surprisal +
                     s(surprisal, bs="cr", k=20)+
                     ti(freq, bs="cr") + 
                     ti(len, bs="cr")+
                     prev_surp +
                     s(prev_surp, bs="cr", k=20)+
                     ti(prev_freq, bs="cr")+
                     ti(prev_len, bs="cr")

#no hierarchical, has freq x len interaction
formula_interact <- rt ~ s(surprisal, bs="cr", k=20)+
                     ti(freq, bs="cr") + 
                     ti(len, bs="cr")+
                     ti(freq,len, bs="cr")+
                     s(prev_surp, bs="cr", k=20)+
                     ti(prev_freq, bs="cr")+
                     ti(prev_len, bs="cr")+
                     ti(prev_freq, prev_len, bs="cr")

@@

gam_gpt_3_hf <- gam(formula3_interact, data=subset(gpt_mean_data,freq > 2), method="REML")
gam_gpt_3_lf <- gam(formula3_interact, data=subset(gpt_mean_data,freq <= 2), method="REML")

gam_gpt_2_hf <- gam(formula2_interact, data=subset(gpt_mean_data,freq > 2), method="REML")
gam_gpt_2_lf <- gam(formula2_interact, data=subset(gpt_mean_data,freq <= 2), method="REML")

gam_ngram_2 <- gam(formula_no_interact, data=ngram_mean_data, method="REML")
gam_grnn_2 <- gam(formula_no_interact, data=grnn_mean_data, method="REML")
gam_txl_2 <- gam(formula_no_interact, data=txl_mean_data, method="REML")
gam_gpt_no_interact <- gam(formula_no_interact, data=gpt_mean_data, method="REML")
gam_gpt_no_interact_plus_linear_surprisal <- gam(formula_no_interact_plus_linear_surprisal, data=gpt_mean_data, method="REML")

@@

summary(getViz(gam_gpt_3_hf))
print(plot(getViz(gam_gpt_3_hf)))
print(plot(getViz(gam_gpt_2_hf)))

summary(getViz(gam_gpt_3_lf))
print(plot(getViz(gam_gpt_3_lf)))

summary(gam_gpt_no_interact_plus_linear_surprisal)
```
